Turbulence in compact to giant H~II regions

### 2022-12-19 strucfunc_paper.tex
Shorten abstract and add keywords

% Abstract of the paper
\begin{abstract}
  % Context
  Radial velocity fluctuations on the plane of the sky
  are a powerful tool for studying the turbulent dynamics of emission line regions.
  % What we did
  We conduct a systematic statistical analysis
  of the observed \halpha\ centroid velocity field for
  a diverse sample of 9 \hii{} regions,
  spanning two orders of magnitude in size and luminosity,
  that are located in the Milky Way and other Local Group galaxies
  % How we did it
  By fitting a simple analytic model to the second-order spatial structure function
  of the velocity fluctuations, we extract three fundamental parameters:
  the plane-of-sky velocity dispersion,
  the correlation length,
  and the power law slope.
  We determine the credibility limits for these parameters in each region,
  taking into account the observational limitations of noise,
  atmospheric seeing, and the finite map size.
  % What we found
  The plane-of-sky velocity dispersion is found to be a better diagnostic
  of turbulent motions than the line width, especially for lower
  luminosity regions where the turbulence is subsonic.
  The correlation length of velocity fluctuations is found to
  be always roughly 2\% of the \hii{} region diameter,
  implying that turbulence is driven on relatively small scales.
  No evidence is found for a steepening of the power law slope of the structure function
  in the transition from subsonic to supersonic turbulence,
  which may be due to the countervailing effect of projection smoothing.
  Ionized density fluctuations are too large to be explained by the action
  of the turbulence in most cases, with the exception of the highest
  luminosity sources.
  A variety of behaviors are seen on scales larger than the correlation length,
  with only a minority of sources showing evidence for homogeneity on the largest scales.
  % In the statistical analysis we obtain the second-order structure function of the observed \halpha\ centroid velocity field.
  % We proposed a model for the structure function which takes into account observational constraints like the seeing (\(s_0\)), instrumental noise (\(B_{\text{noise}}\)) and size of the field of view (\(L\)).
  % The turbulent velocity field parameters like the velocity dispersion of the centroid velocity (\(\sigma\pos\)), the autocorrelation length (\(r_0\)) and a power-law index (\(m\)) are also considered in our model.
  % We fit our model to the observational structure function using a non-linear regression analysis which allow us to derive the parameters representing each velocity field.
  % The results for the 9 \hii{} regions are: \(\num{0.2} < s_0 \text{(FWHM)} < \SI{3.0}{arcsec}\), \(\num{0.003} < B_{\text{noise}} < \SI{6.0}{km^{-2}.s^{-2}}\),  \(\num{3} < \sigma\pos < \SI{19}{km.s^{-1}}\), \(\num{0.07} < r_0 < \SI{12}{pc}\) and \(\num{0.7}< m < \num{1.5}\). 
  % The derived parameters are used to determine scaling relations between the physical properties of the regions like \halpha\ luminosity (\(L(H_{\alpha})\)), diameter (\(D\)) and the mean non-thermal linewidth (\(\langle \sigma_{los} \rangle\)).
  % We find that these relations are \(\sigma\pos \propto L(H_{\alpha})^{0.28 \pm 0.10}\) and \(r_0 \propto D^{0.95 \pm 0.32}\).
  % The \(\sigma\pos\) and \(\langle \sigma_{los} \rangle\) increase following a linear relation.
  % From the previous relations we found that the for our sample the \Mach{} number ranges from \( 0.5 - 2.5\) and that for ionized regions the energy is injected on scales smaller than 10\% of the size of each region.
  % We explain the derived power law slope by considering the effect of projection smearing and emissivity fluctuations.
  % We show that for ionized regions, the latter one, can be related to density fluctuations and use it as a diagnostic to determine the presence of turbulence-induced density fluctuations. 
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
turbulence -- instrumentation: spectrographs -- ISM: HII regions, kinematics and dynamics
\end{keywords}

>>>>

% Abstract of the paper
\begin{abstract}
  % Context
  Radial velocity fluctuations on the plane of the sky
  are a powerful tool for studying the turbulent dynamics of emission line regions.
  % What we did
  We conduct a systematic statistical analysis
  of the \halpha{} velocity field for
  a diverse sample of 9 \hii{} regions,
  spanning two orders of magnitude in size and luminosity,
  located in the Milky Way and other Local Group galaxies.
  % How we did it
  By fitting a simple model to the second-order spatial structure function
  of velocity fluctuations, we extract three fundamental parameters:
  the velocity dispersion,
  the correlation length,
  and the power law slope.
  We determine credibility limits for these parameters in each region,
  accounting for observational limitations of noise,
  atmospheric seeing, and the finite map size.
  % What we found
  The plane-of-sky velocity dispersion is found to be a better diagnostic
  of turbulent motions than the line width, especially for lower
  luminosity regions where the turbulence is subsonic.
  The correlation length of velocity fluctuations is found to
  be always roughly 2\% of the \hii{} region diameter,
  implying that turbulence is driven on relatively small scales.
  No evidence is found for any steepening of the structure function
  in the transition from subsonic to supersonic turbulence,
  possibly due to the countervailing effect of projection smoothing.
  Ionized density fluctuations are too large to be explained by the action
  of the turbulence in all but the highest luminosity sources.
  A variety of behaviors are seen on scales larger than the correlation length,
  with only a minority of sources showing evidence for homogeneity on the largest scales.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
HII regions -- ISM: kinematics and dynamics -- turbulence 
\end{keywords}
